---
title: "Netflix: Serving delicous cheeseburgers that brings fans back for more"
format:
  html:
    theme: pulse
    theme-accent: "#D81F26"
    toc: true
    toc-depth: 3
    sections: true
    css: custom.css
    code-fold: true
    code-summary: "Show the code"
    code-tools:
      toggle: true
      source: true
      caption: "code"
---
<style>
body {
  font-family: 'Lato', sans-serif;
}
</style>

**New York, NY, September 30, 2025:** During this past decade, viewers have been showing more and more interest in both foreign and non-English films like the award-winning film *Parasite*, and the massively popular show *Squid Games* (both currently offered on Netflix). To keep up with this growing demand, Netflix has invested and expanded globally, partnering with companies and studios to add high-quality films and shows to its offerings. 

This week, *KPop Demon Hunters*, *Wayward*, *She said Maybe*, and *Billionaires' Bunker* are leading the top 10 on its' platform for English movies, English shows, non-English Movies and non-English Shows, respectively. Netflix continues to dominate the top 10 on its' platform this week as every #1 title is a Netflix Original. This leads to some further questions about Netflix and their performance between its English and non-English content. Even though all of these films and movies are at #1 in their category, how popular are they compared to each other? And is Netflix seeing non-English content outpacing English content in terms of growth and viewership?

## Aquiring Data

In order to answer these questions, we will use the language R to set up and analyze our findings. First, let's prepare the foundation to answer these important questions. There are two files we will use to analyse and find our answers, from [Netflix's TuDum Top 10](https://www.netflix.com/tudum/top10){style="color: red;"}. The two files are Global Top 10 and Country-wide Top 10, both important for finding popularity of films and shows on a large and smaller scale.

```{r}
#| echo: true
#| include: true
#| output: false

# Create folder
if (!dir.exists(file.path("data", "mp01"))) {
  dir.create(file.path("data", "mp01"), showWarnings = FALSE, recursive = TRUE)
}

# Download global file
global_file <- file.path("data", "mp01", "global_top10_alltime.csv")
if (!file.exists(global_file)) {
  download.file("https://www.netflix.com/tudum/top10/data/all-weeks-global.tsv",
                destfile = global_file)
}

# Download country file
country_file <- file.path("data", "mp01", "country_top10_alltime.csv")
if (!file.exists(country_file)) {
  download.file("https://www.netflix.com/tudum/top10/data/all-weeks-countries.tsv",
                destfile = country_file)
}
```

We will use multiple libraries to analyze as well, such as *tidyverse, knitr, and DT*.

```{r}
#| echo: true
#| include: true
#| output: false

# Download libraries
packages <- c("tidyverse", "knitr", "kableExtra", "DT")

for (pkg in packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, repos = "https://cloud.r-project.org/")
    library(pkg, character.only = TRUE)
  }
}

library(tidyverse)
library(knitr)
library(kableExtra)
library(DT)

```

## Data Importing and Setup

### Importing and Cleaning

After downloading the files, and setting up the libraries, it's time to import these files and get a feeling of the data.

```{r}
#| echo: true
#| results: hold
#| include: true
#| output: true
# Read data files
invisible(suppressMessages(GLOBAL_TOP_10 <- read_tsv(global_file)))


#Describe the data, with four instances

summary_tbl <- tibble(
  Column = names(GLOBAL_TOP_10),
  Type = sapply(GLOBAL_TOP_10, class),
  Example = sapply(GLOBAL_TOP_10, function(x) toString(head(unique(x), 4)))
)

kable(summary_tbl, caption = "Global Top 10 Overview")

cat("Number of rows:", nrow(GLOBAL_TOP_10), "\n\n")
```

Everything looks good at an initial glance. However, it's always important to make sure that the formatting within a data set is correct, or there can be issues. These missing values (commonly known as NA or Not Available) do not follow the formatting that R detects. There are multiple ways to clean and format data, such as
<span class="custom-tooltip">mutating
<span class="custom-tooltiptext">Adds or modifies columns in a data frame by computing new variables.</span>
</span>
a column within the data to replace variables (i.e. replacing N/A with NA). A column within the data to replace variables (i.e. replacing N/A with NA) or doing so when initially importing the file.


```{r}
#| echo: true
#| include: true
#| output: false

# Count N/A and NA strings beforemutation
na_string_count_before <- sum(GLOBAL_TOP_10$season_title %in% c("N/A", "NA"), na.rm = TRUE)
na_count_before <- sum(is.na(GLOBAL_TOP_10$season_title))

# Mutating the season_title column
GLOBAL_TOP_10 <- GLOBAL_TOP_10 |>
  mutate(season_title = if_else(
    is.na(season_title)
    | season_title == 'N/A',
    NA_character_,
    season_title
  ))
# Replacing ALL N/A with NA  

COUNTRY_TOP_10 <- read_tsv(country_file, na = c("N/A", "NA"))


```
Now that we changed the data, lets quickly look if the NA values changed.
```{r}
#| echo: true
#| results: hold
#| include: true
#| output: true


# Count NAs after mutation
na_count_after <- sum(is.na(GLOBAL_TOP_10$season_title))

cat("In 'season_title' column:\n")
cat(" - Number of 'N/A' or 'NA' strings before mutation:", na_string_count_before, "\n")
cat(" - Number of NA values before mutation:", na_count_before, "\n")
cat(" - Number of NA values after mutation:", na_count_after, "\n")
```
The number of NA and N/A values being the same as the NA values after mutation is good. We can now move on to the next step.



### Initial Data Exploration

#### Table View of data
Lets look at a larger sample of the data, since there are 8,800 rows table:
```{r}
format_titles <- function(df){
    colnames(df) <- str_replace_all(colnames(df), "_", " ") |> str_to_title()
    df
}

GLOBAL_TOP_10 |> 
  mutate(`runtime_(minutes)` = round(60 * runtime)) |>
  select(-runtime) |>
  format_titles() |>
  slice_sample(n = 25) |> 
  datatable(options = list(pageLength = 5,
    lengthMenu = c(5, 10, 20, 25),
    searching = FALSE, info = FALSE)) |>
  formatRound(c('Weekly Hours Viewed', 'Weekly Views'))
```


```{r, include=FALSE}
#question 1
num_country <- COUNTRY_TOP_10 |>
  summarize(n_distinct(country_name))

top_non_eng_film <- GLOBAL_TOP_10 |>
  filter(category == 'Films (Non-English)') |>
  select(show_title, cumulative_weeks_in_top_10) |>
  slice_max(cumulative_weeks_in_top_10, n = 1)

#Question 2
top_film_title <- top_non_eng_film$show_title[1]
top_film_weeks <- top_non_eng_film$cumulative_weeks_in_top_10[1]

#Question 6
less_200 <- COUNTRY_TOP_10 |> group_by(country_name) |> summarise(total_weeks = n_distinct(week), .groups = "drop") |> filter(total_weeks < 200) 

country_ceased <- less_200$country_name 

#Number of weeks before operations stopped
weeks_ceased <- less_200$total_weeks
last_week <- COUNTRY_TOP_10 |> group_by(country_name) |> summarise(last_week = max(week), .groups = "drop") 
ceased_info <- less_200 |> inner_join(last_week, by = "country_name") 
cease_date <- format(ceased_info$last_week, "%B %d, %Y")
```

Clearly, the data varies a lot. After all, Netflix operates in **`r num_country[[1]]`** countries.[^num_countries] However, Netflix did cease its' operations in **`r country_ceased`** on `r cease_date`, only operating there for a total of **`r weeks_ceased`** weeks this year.[^cease_service]   Essentially, that means that 


The top global non-English film is *`r top_film_title`*, which spent **`r top_film_weeks` weeks** in the top 10.[^top_film_weeks] 

 
with the data spanning years, data including TV and Films, the specific season and whether they are English or non-English. Netflix after all, 
Some further exploration is needed to understand this data.









## Exploratory Analysis







[^num_countries]: 
Code for total number of countries:  
    ```{r}
#Question 1
num_country<- COUNTRY_TOP_10 |>
  summarize(n_distinct(country_name))
    ```

[^top_film_weeks]:  
Code for top global non-English film:
    ``` {r}
#| output: False
# Question 2
top_non_eng_film <- GLOBAL_TOP_10 |>
  filter(category == 'Films (Non-English)') |>
  select(show_title, cumulative_weeks_in_top_10) |>
  slice_max(cumulative_weeks_in_top_10, n = 1)


top_film_title <- top_non_eng_film$show_title[1]
top_film_weeks <- top_non_eng_film$cumulative_weeks_in_top_10[1]

    ```
    
[^cease_service]:  
Code for which country Netlfix stopped service:
    ``` {r}
#Question 6
less_200 <- COUNTRY_TOP_10 |> group_by(country_name) |> summarise(total_weeks = n_distinct(week), .groups = "drop") |> filter(total_weeks < 200) 
    

country_ceased <- less_200$country_name 
weeks_ceased <- less_200$total_weeks

last_week <- COUNTRY_TOP_10 |> group_by(country_name) |> summarise(last_week = max(week), .groups = "drop") 

ceased_info <- less_200 |> inner_join(last_week, by = "country_name") 

#Formatting
cease_date <- format(ceased_info$last_week, "%B %d, %Y")
    ```
